### 2024-05-26 getting-started.qmd
20240526 - variable names and logical operators

>>>>

## Variable Names {#sec-variableNames}

To see the names of variables in a data frame, use the following syntax:

```{r}
names(nfl_players)
```

## Logical Operators {#sec-logicalOperators}

### Is Equal To: `==` {#sec-logicalOperatorEqual}

```{r}
nfl_players$position_group == "RB"
```

### Is Not Equal To: `!=` {#sec-logicalOperatorNotEqual}

```{r}
nfl_players$position_group != "RB"
```

### Is Greater Than: `>` {#sec-logicalOperatorGreaterThan}

```{r}
nfl_players$weight > 300
```

### Is Less Than: `<` {#sec-logicalOperatorLessThan}

```{r}
nfl_players$weight < 300
```

### Is Greater Than or Equal To: `>=` {#sec-logicalOperatorGreaterThanEqual}

```{r}
nfl_players$weight >= 300
```

### Is Less Than or Equal To: `<=` {#sec-logicalOperatorLessThanEqual}

```{r}
nfl_players$weight <= 300
```

### Is In a Value of Another Vector: `%in%` {#sec-logicalOperatorInVector}

```{r}
nfl_players$position_group %in% c("QB","RB","WR")
```

### Is Not In a Value of Another Vector: `!(%in%)` {#sec-logicalOperatorNotInVector}

```{r}
!(nfl_players$position_group %in% c("QB","RB","WR"))
```

### Is Missing: `is.na()` {#sec-logicalOperatorMissing}

```{r}
is.na(nfl_players$college_name)
```

### Is Not Missing: `!is.na()` {#sec-logicalOperatorNotMissing}

```{r}
!is.na(nfl_players$college_name)
```

### And: `&`{#sec-logicalOperatorAnd}

```{r}
nfl_players$position_group == "RB" & nfl_players$weight > 230
```

### Or: `|` {#sec-logicalOperatorOr}

```{r}
nfl_players$position_group == "RB" | nfl_players$weight > 230
```
